---
title: "Decision tree"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(dplyr)

rm(list = ls())
```

# Assign Buckets to Internationals

### 1. Create a Dataframe of all possible input combinations

```{r}
# Create DF with all possible combinations
relocating_to_city_code <- c("DE-HAMBURG","DE-BERLIN","DE-MUENCHEN","DE-KOELN", "DE-BONN", "DE-STUTTGART", "DE-DUESSELDORF", "DE-FRANKFURT", "DE-DORTMUND")
country_type <- c("Third-country", "EU", "Privileged", "GB", "Switzerland")
visa_status <- c("visa", "job seeker", "valid rp", "blue card", "none")
income_range <- c("0-30.000", "30.001-40.560", "40.561-52.000", "52.001-59.400", "59.401-70.000", "70.001-80.000", "80.001-90.000", ">90.000")
family_relocating_dummy <- c("Yes","No")

col_names <- c("relocating_to", "country_type", "visa_status", "income_range", "family_relocating")

df <- expand.grid(relocating_to_city_code, country_type, visa_status, income_range, family_relocating_dummy)
colnames(df) <- col_names

write.csv(df, file="decisiontree.csv", row.names = FALSE)
```

### 2. For each possible combination, define if a bucket gets assigned

(1 = Yes, 0 = No)

```{r}
Newemployee_df <- read.csv("../input/DecisionTree - NewEmployee.csv")

# Duplicate the df so we can split into training/test 
newempl2_df <- rbind(Newemployee_df, Newemployee_df)

# Generate a random list of index from 1 to 1309 (i.e. the maximum number of rows)
shuffle_index <- sample(1:nrow(newempl2_df))
#  use this index to shuffle the titanic dataset.
newempl2_df <- newempl2_df[shuffle_index, ]

# Convert NA to 0
newempl2_df[is.na(newempl2_df)] <- 0

head(newempl2_df)
```

### 3. Train a statistical model that estimates the probability of a bucket assignment, depending on the characteristics

```{r}
## Create train / test set

create_train_test <- function(data, size = 0.8, train=TRUE) {
  n_row = nrow(data)
  total_row = size * n_row
  train_sample <- 1:total_row
  if (train == TRUE) {
    return (data[train_sample, ])
  } else {
    return (data[-train_sample, ])
  }
}
```

```{r}
# x-vars
xvars <- colnames(newempl2_df %>% select(relocating_to:family_relocating))

# get all buckets
yvars <- colnames(newempl2_df %>% select(general_Family:Registration))

# select a random sample
#yvar <- sample(yvars, 1)
yvar <- "ZAV"

# take one bucket as yvar
model_df <- newempl2_df %>% select(xvars, yvar)

data_train <- create_train_test(model_df, 0.8, train = TRUE)
data_test <- create_train_test(model_df, 0.8, train = FALSE)

print(paste('Decision Tree for:',yvar))
```


```{r}
library(rpart)
library(rpart.plot)
fit <- rpart(ZAV~., data = data_train, method = 'class')
rpart.plot(fit, extra = 106)
```

- At the top, it is the overall probability of the bucket ZAV. It shows the proportion of users that need a ZAV (8%) 

- The top node asks whether the user already has a valid rp (or blue card, job seeker, visa). If yes, then you go down to the root's left child node (depth 2). 80% percent have a valid rp and the probability of needing the ZAV is 0.

### 4. Predict the buckets for our Internationals

```{r}
# Load userdata
load("../../../Analytics/script/cleaned_data.RData")
```

Create a function that takes as input the user characteristics:

- Nationality
- Family relocating
- Relocating to
- Income range
- Visa status (visa, blue card, RP)
- Employment status (new employment, extension)

... based on the trained models, check if a bucket should be assigned (yes / no)

and returns the buckets that are assigned to that user.

```{r}
predict_df <- international_df_clean %>%
  filter(code_relocating_city %in% relocating_to_city_code) %>%
  filter(wasdeleted == FALSE) %>%
  mutate(
    name = name,
    #family_relocating = as.factor(ifelse(is.na(family_status_id), "No", "Yes")),
    family_relocating = as.factor(ifelse(family_status_id == 1, "No", "Yes")),
    relocating_to = as.factor(code_relocating_city),
    nationality = as.factor(country_type),
    visa_status = as.factor("none"),
    income_range = as.factor(income_group)
  ) %>% select(c(email,family_relocating,relocating_to,nationality,visa_status,income_range))
```

```{r}
predict_unseen <-predict(fit, predict_df, type = 'class')

predict_df$zav <- predict_unseen

predict_df %>% sample_n(20)
```


